Supporting Information

### 2015-08-18 si.Rmd
try 8 clusters

---
title: "Supporting Information"
csl: csl/the-plant-journal.csl
header-includes: \usepackage{graphicx}
output:
  BiocStyle::html_document:
    fig_caption: yes
    force_captions: yes
    highlight: pygments
    keep_md: yes
    number_sections: yes
  word_document:
    fig_caption: yes
bibliography: bib/test.bib
---

@@

knitr::opts_chunk$set(fig.path='figures/',
               cache.path='cache/',
               dev=c("cairo_pdf"),
               fig.width=6.614,
               fig.height=6.614,
               fig.align = 'center',
               dpi=300,
               fig.show='hold',
               cache=FALSE,
               echo=FALSE,
               results="hide",
               message=FALSE,
               warning=FALSE)

@@

@@

```{r mfuzz}
figCount <- incCount(figCount, "f_mfuzzCentroids")
print(f_mfuzzCentroids)

>>>>

---
title: "Supporting Information"
csl: csl/the-plant-journal.csl
header-includes: \usepackage{graphicx}
output:
  BiocStyle::html_document:
    fig_caption: yes
    force_captions: yes
    highlight: pygments
    keep_md: yes
    number_sections: yes
    dev: svg
  word_document:
    fig_caption: yes
  pdf_document:
    fig_caption: yes
    keep_tex: yes
    number_sections: yes
bibliography: bib/test.bib
---

@@

knitr::opts_chunk$set(fig.path='figures/',
               cache.path='cache/',
               dev=c("svg", "cairo_pdf"),
               fig.width=6.614,
               fig.height=6.614,
               fig.align = 'center',
               dpi=300,
               fig.show='hold',
               cache=FALSE,
               echo=FALSE,
               results="hide",
               message=FALSE,
               warning=FALSE)

@@

``` {r libStats}
tableCount <- incCount(tableCount, "t_libStats")
```

### `r I(pasteLabel("Table", tableCount, "t_libStats"))`

``` {r t_libStats, results = "markup"}
knitr::kable(t_libStats, caption = "Library and sequencing statistics")
```

@@

```{r mfuzz, cache = TRUE}
figCount <- incCount(figCount, "f_mfuzzCentroids")
print(f_mfuzzCentroids)
